Figures

### 2019-06-18 figures/08_exploratory_dotplot.Rmd
fix cut off figure

```{r 08_exploratory_dotplot, echo=FALSE, message=TRUE, eval=TRUE, warning=FALSE}
pred_key <- read.csv("../data/predictor_key.csv", stringsAsFactors = FALSE)

>>>>

```{r 08_exploratory_dotplot, echo=FALSE, message=TRUE, eval=TRUE, warning=FALSE, fig.height=5.5}
pred_key <- read.csv("../data/predictor_key.csv", stringsAsFactors = FALSE)
